Moment Constraints Make Learning Latent-Variable Models Easier

### 2014-01-28 doc/icml2014/intro.tex
Updated background
Updates to paper

\begin{figure*}
  \centering
  \input{figures/approach.tikz}
  \caption{Overview of approach}
\end{figure*}

>>>>

\begin{figure}[t]
  \label{fig:approach}
  \centering
\begin{tikzpicture}

% Import grid.
%\node[scale=0.9] (step0) at (0,0) {\input{figures/grid.tikz}};
\node[scale=0.9] (step1) at (0cm,0cm) {\input{figures/grid-outline.tikz}};
\node[scale=0.75, below=0.5 cm of step1.south] { \textbf{Step 1:} Identify bottlenecks};
\node[scale=0.9] (step2) at (5cm,0cm) {\input{figures/factors.tikz}};
\node[scale=0.75, below=0.5 cm of step2.south] { \textbf{Step 2:} Optimize piecewise likelihoods};

\draw[-latex] (step1) -- (step2);

\end{tikzpicture}
  \caption{Overview of approach}
\end{figure}
